Meta-analysis

### 2019-11-05 05_MetaAnalysis.Rmd
Some LMmodels on slim data

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)

@@

### Estimating variance for trials without reported error

@@

#### Random effects model to predict trial variance
Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.

@@

## Between trial variation

@@

>>>>

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)

@@

## Estimating variance for trials without reported error

@@

### Random effects model to predict trial variance
Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.

@@

### Between trial variation

@@

## Preliminary meta-analysis

```{r}
slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")

m1 <- lmer(grain_yield.t.ha*1000 ~ factor(total_fungicide) + (factor(total_fungicide) | trial_ref), data = slim_PM_dat)

m2 <- lmer(grain_yield.t.ha*1000 ~ factor(total_fungicide) + (1 | trial_ref), data = slim_PM_dat)

anova(m1,m2)

m3 <- lmer(log(grain_yield.t.ha*1000) ~ factor(total_fungicide) + (factor(total_fungicide) | trial_ref), data = slim_PM_dat)

anova(m1, m3)
summary(m3)

```{r}
